---
title: "Verification GEOtop point simulation"
author: "Johannes Brenner"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
runtime: shiny
---

***

This R Markdown document is made interactive using Shiny. To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

***

```{r, include=FALSE}

if(!require(AnalyseGeotop))
{
  if(!require("devtools"))
  {
    install.packages(devtools)
    require("devtools")
  }
  install_github("AnalyseGeotop", "JBrenn")
  require("AnalyseGeotop")
}

if(!require("dygraphs"))
{
  install.packages(dygraphs)
  require("dygraphs")
}

if(!require("hydroGOF"))
{
  install.packages(hydroGOF)
  require("hydroGOF")
}

if(!require("ggplot2"))
{
  install.packages(ggplot2)
  require("ggplot2")
}

#wpath <- "/run/user/1000/gvfs/smb-share:server=sdcalp01.eurac.edu,share=data2/Simulations/Simulation_GEOtop_1_225_ZH/Vinschgau/SimTraining/BrJ/HiResAlp/1D/Montecini_pnt_1_225_B2_007/"
#wpath <- "/run/user/1000/gvfs/smb-share:server=sdcalp01.eurac.edu,share=data2/Simulations/Simulation_GEOtop_1_225_ZH/Vinschgau/SimTraining/BrJ/HiResAlp/1D/Montecini_pnt_1_225_P2_003/"
#wpath <- "/run/user/1000/gvfs/smb-share:server=sdcalp01.eurac.edu,share=data2/Simulations/Simulation_GEOtop_1_225_ZH/Vinschgau/SimTraining/BrJ/MonaLisa/1D/Kaltern/sim006/"
#wpath <- "/run/user/1000/gvfs/smb-share:server=sdcalp01.eurac.edu,share=data2/Simulations/Simulation_GEOtop_1_225_ZH/Vinschgau/SimTraining/BrJ/HiResAlp/1D/B2_P2_Dynamic/B2_BrJ_017_DVM_002/"
#wpath <- "/run/user/1000/gvfs/smb-share:server=sdcalp01.eurac.edu,share=data2/Simulations/Simulation_GEOtop_1_225_ZH/Vinschgau/SimTraining/BrJ/MonaLisa//1D/DOMEF_1500/sim000/"
wpath <- "/run/user/1000/gvfs/smb-share:server=sdcalp01.eurac.edu,share=data2/Simulations/Simulation_GEOtop_1_225_ZH/Vinschgau/SimTraining/BrJ/MonaLisa//1D/DOMES_1500/sim000/"
#wpath <- "/run/user/1000/gvfs/smb-share:server=sdcalp01.eurac.edu,share=data2/Simulations/Simulation_GEOtop_1_225_ZH/Vinschgau/SimTraining/BrJ/MonaLisa//1D/DOPAS_1500/sim000/"

# obs data
load(file.path(wpath, "obs", "observation.RData"))

if (!exists("obs")) obs <- observation
names(obs) <- c("hour", "day")
#time(obs$hour) <- as.POSIXlt(time(obs$hour))

# sim data
if (file.exists(file.path(wpath,"PointOutValidation.RData"))) {
  load(file.path(wpath,"PointOutValidation.RData"))
} else {
  var_out <- GEOtop_ReadValidationData(wpath = wpath, obs = obs, save_rData = T)
}

varout <- var_out

# adjust datetime: observations -1 hour
time(obs$hour) <- as.POSIXlt(time(obs$hour))
time(obs$hour)$mday <- time(obs$hour)$mday - 1
time(obs$day) <- time(obs$day) - 1

# get hourly lag between obs and sim

if ("air_temperature" %in% names(obs$hour)) {
  ccf_temp <- stats::ccf(var_out[["air_temperature"]], obs$hour[,"air_temperature"], plot = F, na.action = na.pass)
  lag <- round(ccf_temp$acf[which.max(ccf_temp$acf)],0)
  time(obs$hour)$hour <- time(obs$hour)$hour + lag
}

# load lookup table
data("lookup_tbl_observation")

```

#### Interactive Inputs

```{r, echo=FALSE}
inputPanel(
  #textInput(inputId = "simFolder", label = "Simulation folder", value = "")
  
  selectInput(inputId = "variable", label = "discover variable", choices = dimnames(obs$day)[[2]]),
  
  selectInput(inputId = "add_variable", label = "additional variable (sim)", choices = c(NA,dimnames(obs$day)[[2]]), selected = "rainfall_amount"),
  
  radioButtons(inputId = "aggregation", label = "aggregation", choices = c("hour","day","month"), selected = "day", inline = FALSE),
  
  radioButtons(inputId = "flux_amount", label = "flux or amount", choices = c("flux","amount"), selected = "flux", inline = FALSE),
  
  downloadButton(outputId = "downloadData", label = "Download")
  
  # radioButtons(inputId = "cum", label = "cumulated or time series", choices = c("time series","cumulated over time"), selected = "time series", inline = FALSE)
  
)

```

***

#### Time Series Plot

Cumulated timeseries are only provided for daily data aggregation. Check if your variable of interest is a flux or an amount!

```{r, echo=FALSE}

renderDygraph({
  
  name <- input$variable
  if (grepl("soil_moisture_content",input$variable)) name <- "soil_moisture_content"
  if (grepl("soil_temperature", input$variable)) name <- "soil_temperature"
  if (grepl("liquid_soil_water_pressure", input$variable)) name <- "liquid_soil_water_pressure"
  
  if (!is.na(input$add_variable)) 
  {
    add_name <- input$add_variable
    if (grepl("soil_moisture_content",input$add_variable)) add_name <- "soil_moisture_content"
    if (grepl("soil_temperature", input$add_variable)) add_name <- "soil_temperature"
    if (grepl("liquid_soil_water_pressure", input$add_variable)) add_name <- "liquid_soil_water_pressure"
    add_units <- lookup_tbl_observation$unit[lookup_tbl_observation$obs_var==add_name]
  }

  units <- lookup_tbl_observation$unit[lookup_tbl_observation$obs_var==name]

  if (input$aggregation=="hour" | input$aggregation=="day")
  {
    observation <- obs[[input$aggregation]][,input$variable]
  } else observation <- obs[["day"]][,input$variable]
  
  simulation <- varout[[input$variable]]
  if (!is.na(input$add_variable))
    add_var    <- varout[[input$add_variable]] * (-1)
  
  if (input$aggregation=="day" & input$flux_amount=="flux") simulation <- aggregate(simulation, as.Date(time(simulation)), mean, na.rm=T) 
  if (input$aggregation=="day" & input$flux_amount=="amount") simulation <- aggregate(simulation, as.Date(time(simulation)), sum, na.rm=F)
  if (input$aggregation=="month" & input$flux_amount=="flux") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), mean, na.rm=T)
    observation <- aggregate(observation, as.yearmon(time(observation)), mean, na.rm=T)
  } 
  if (input$aggregation=="month" & input$flux_amount=="amount") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), sum, na.rm=F)
    observation <- aggregate(observation, as.yearmon(time(observation)), sum, na.rm=F)
  } 
  
    if (!is.na(input$add_variable))
    {
      if (input$aggregation=="day")  add_var <- aggregate(add_var, as.Date(time(add_var)), sum, na.rm=T) 
      if (input$aggregation=="month")  add_var <- aggregate(add_var, as.yearmon(time(add_var)), sum, na.rm=T) 
    }

  
 # data <- merge(observation, simulation)
  
#   if (input$cum == "cumulated over time" & input$aggregation=="day")
#   {
#     if (input$variable=="evapotranspiration" | input$variable=="sensible_heat_flux_in_air" | input$variable=="latent_heat_flux_in_air") {
#       data <- merge(observation, simulation)
#       data <- window(x = data, start = as.Date("30-04-2011",format="%d-%m-%Y"), end = as.Date("17-04-2013", format="%d-%m-%Y"))
#       data <- zoo(na.approx.default(data), time(data))
#       data <- cumsum(data) 
#     } else {
#       data <- merge(observation, simulation)
#       data <- data[!is.na(data$observation),]
#       data <- cumsum(data)
#     }
# 
#     
#     dygraph(data, ylab=paste("[",units,"]",sep="")) %>%
#       dyRangeSelector() %>%
#       dyRoller()
#   } else {
  
# from POSIXlt to POSIXct  
 time(observation) <- as.POSIXct(time(observation))
 if (!is.na(input$add_variable)) time(add_var) <- as.POSIXct(time(add_var))
 time(simulation) <- as.POSIXct(time(simulation))
  
  if (is.na(input$add_variable)) {
    data <- merge(observation, simulation)
    names(data) <- c("observation", "simulation")
  } else {
    data <- merge(add_var, observation, simulation)
    names(data) <- c( "additional var", "observation", "simulation")
  }

  if (is.na(input$add_variable)) {
      dygraph(data, ylab=paste("[",units,"]",sep="")) %>%
      dyRangeSelector() %>%
      dyRoller()
  } else {
      dygraph(data, ylab=paste("[",units,"]",sep="")) %>%
      dyRangeSelector() %>%
      dyRoller() %>%
      dySeries(name = "additional var", axis = "y2", stepPlot = TRUE, fillGraph = TRUE, label = paste("[-",add_units,"]",sep=""))
  }  
 
    
#  }
 
})

```
  
***

####Summary Table on Goodness of Fit (GOF)

Measures for GOF are given for seasons and for the whole data series. Calculation were performed with the hydroGOF R-Package. Type ?gof in RStudio for information on specific GOFs.

```{r, echo=FALSE}

renderDataTable({
 if (input$aggregation=="hour" | input$aggregation=="day")
  {
    observation <- obs[[input$aggregation]][,input$variable]
  } else observation <- obs[["day"]][,input$variable]
  
  simulation <- varout[[input$variable]]
  
 if (input$aggregation=="day" & input$flux_amount=="flux") simulation <- aggregate(simulation, as.Date(time(simulation)), mean, na.rm=T) 
  if (input$aggregation=="day" & input$flux_amount=="amount") simulation <- aggregate(simulation, as.Date(time(simulation)), sum, na.rm=F)
  if (input$aggregation=="month" & input$flux_amount=="flux") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), mean, na.rm=T)
    observation <- aggregate(observation, as.yearmon(time(observation)), mean, na.rm=T)
  } 
  if (input$aggregation=="month" & input$flux_amount=="amount") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), sum, na.rm=F)
    observation <- aggregate(observation, as.yearmon(time(observation)), sum, na.rm=F)
  } 
  
  time(observation) <- as.POSIXct(time(observation))
  time(simulation) <- as.POSIXct(time(simulation))
  
  data <- merge(observation, simulation)
  
  gofs <- gof(sim = data$simulation, obs=data$observation, na.rm = T)
  gofs <- as.data.frame(gofs)
  names(gofs) <- "YEAR"
  gofs$GOF <- dimnames(gofs)[[1]]
  
  mon <- as.numeric(format(time(data), "%m"))
  
  datadjf <-  data[mon==12 | mon==1 | mon==2,]
  gofs$DJF <-  c(gof(sim = datadjf$simulation, obs=datadjf$observation, na.rm = T))
  datamam <-  data[mon==3 | mon==4 | mon==5,]
  gofs$MAM <-  c(gof(sim = datamam$simulation, obs=datamam$observation, na.rm = T))
  datajja <-  data[mon==6 | mon==7 | mon==8,]
  gofs$JJA <-  c(gof(sim = datajja$simulation, obs=datajja$observation, na.rm = T))
  datason <-  data[mon==9 | mon==10 | mon==11,]
  gofs$SON <-  c(gof(sim = datason$simulation, obs=datason$observation, na.rm = T))
  
  gofs <- gofs[,c(2,3,4,5,6,1)]

}, options = list(pageLength=5, lengthMenu=c(5, 10, 15, 20)))


# data download
  output$downloadData <- downloadHandler(filename = function() { 
    paste(input$variable, "_", input$aggregation, ".csv", sep="") 
    },
    content = function(file) {
  if (input$aggregation=="hour" | input$aggregation=="day") {
    observation <- obs[[input$aggregation]][,input$variable]
  } else { observation <- obs[["day"]][,input$variable] }
  
  simulation <- varout[[input$variable]]
  
  if (input$aggregation=="day" & input$flux_amount=="flux") simulation <- aggregate(simulation, as.Date(time(simulation)), mean, na.rm=T) 
  if (input$aggregation=="day" & input$flux_amount=="amount") simulation <- aggregate(simulation, as.Date(time(simulation)), sum, na.rm=F)
  if (input$aggregation=="month" & input$flux_amount=="flux") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), mean, na.rm=T)
    observation <- aggregate(observation, as.yearmon(time(observation)), mean, na.rm=T)
  } 
  if (input$aggregation=="month" & input$flux_amount=="amount") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), sum, na.rm=F)
    observation <- aggregate(observation, as.yearmon(time(observation)), sum, na.rm=F)
  } 
  
  if (input$aggregation=="hour")
  {
      time(observation) <- as.POSIXct(time(observation))
      time(simulation) <- as.POSIXct(time(simulation))
  }
  
  data <- merge(observation, simulation)
  if (input$aggregation=="month") datetime <- format(time(data), "%Y-%m") else datetime <- time(data)

  df <- data.frame(datetime = datetime, coredata(data))
  write.csv(df, file, sep=",", quote=F, row.names = F) 
    })

```

***

####Scatterplot

```{r, echo=FALSE}

renderPlot({
  
    name <- input$variable
    if (grepl("soil_moisture_content",input$variable)) name <- "soil_moisture_content"
    if (grepl("soil_temperature", input$variable)) name <- "soil_temperature"
    if (grepl("liquid_soil_water_pressure", input$variable)) name <- "liquid_soil_water_pressure"
    
    units <- lookup_tbl_observation$unit[lookup_tbl_observation$obs_var==name]
    
    if (input$aggregation=="hour" | input$aggregation=="day")
    {
      observation <- obs[[input$aggregation]][,input$variable]
    } else observation <- obs[["day"]][,input$variable]
    
    simulation <- varout[[input$variable]]

    if (input$aggregation=="day" & input$flux_amount=="flux") simulation <- aggregate(simulation, as.Date(time(simulation)), mean, na.rm=T) 
    if (input$aggregation=="day" & input$flux_amount=="amount") simulation <- aggregate(simulation, as.Date(time(simulation)), sum, na.rm=F)
    if (input$aggregation=="month" & input$flux_amount=="flux") 
    {
      simulation <- aggregate(simulation, as.yearmon(time(simulation)), mean, na.rm=T)
      observation <- aggregate(observation, as.yearmon(time(observation)), mean, na.rm=T)
    } 
    if (input$aggregation=="month" & input$flux_amount=="amount") 
    {
      simulation <- aggregate(simulation, as.yearmon(time(simulation)), sum, na.rm=F)
      observation <- aggregate(observation, as.yearmon(time(observation)), sum, na.rm=F)
    } 
    
  time(observation) <- as.POSIXct(time(observation))
  time(simulation) <- as.POSIXct(time(simulation))

    data <- merge(observation, simulation)
    names(data) <- c("observation", "simulation")
    data <- as.data.frame(coredata(data))
    
    ggplot(data = data, aes(x=observation, y=simulation)) +
      geom_point() +
      geom_abline(intercept=0, slope=1, col=rgb(1,0,0,.5), lwd=2)

})     
```
