---
title: "Verification GEOtop point simulation (Caldero/Kaltern)"
author: "Johannes Brenner"
date: "25. Juni 2015"
output: html_document
runtime: shiny
---

***

This R Markdown document is made interactive using Shiny. To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

***

```{r, include=FALSE}

if(!require(AnalyseGeotop))
{
  if(!require(devtools))
  {
    install.packages(devtools)
    require(devtools)
  }
  install_github("AnalyseGeotop", "JBrenn")
  require(AnalyseGeotop)
}

if(!require(dygraphs))
{
  install.packages(dygraphs)
  require(dygraphs)
}

if(!require(hydroGOF))
{
  install.packages(hydroGOF)
  require(hydroGOF)
}

data("PointOutValidation")

data("observations_Caldero")
data("observations_B2")

data("lookup_tbl_observation")

var_out <- sim0001_Caldero

time(Caldero_30min)$mday <- time(Caldero_30min)$mday - 1
time(Caldero_d) <- time(Caldero_d) - 1

obs <- list(hour=Caldero_30min, day=Caldero_d)

```

#### Interactive Inputs

```{r, echo=FALSE}
inputPanel(
  #textInput(inputId = "simFolder", label = "Simulation folder", value = "")
  
  selectInput(inputId = "variable", label = "discover variable", choices = names(Caldero_d), selected = "air_temperature"),
  
  radioButtons(inputId = "aggregation", label = "aggregation", choices = c("hour","day","month"), selected = "day", inline = FALSE),
  
  radioButtons(inputId = "flux_amount", label = "flux or amount", choices = c("flux","amount"), selected = "flux", inline = FALSE),
  
  radioButtons(inputId = "cum", label = "cumulated or time series", choices = c("time series","cumulated over time"), selected = "time series", inline = FALSE)
  
  #submitButton(text = "apply changes")
  
)

```

***

#### Time Series Plot

Cumulated timeseries are only provided for daily data aggregation. Check if your variable of interest is a flux or an amount!

```{r, echo=FALSE}

renderDygraph({
  
  name <- input$variable
  if (grepl("soil_moisture_content",input$variable)) name <- "soil_moisture_content"
  if (grepl("soil_temperature", input$variable)) name <- "soil_temperature"
  if (grepl("liquid_soil_water_pressure", input$variable)) name <- "liquid_soil_water_pressure"
  
  if(name=="soil_moisture_content" & length(strsplit(x = input$variable, split = "_")[[1]])==5) 
    {
      spl <- strsplit(x = input$variable, split = "_")[[1]]
      input$variable <- paste(spl[1],spl[2],spl[3],spl[4], sep = "_")
    }
   
  units <- lookup_tbl_observation$unit[lookup_tbl_observation$obs_var==name]
  
  if (input$aggregation=="hour" | input$aggregation=="day")
  {
    observation <- obs[[input$aggregation]][,input$variable]
  } else observation <- obs[["day"]][,input$variable]
  
  simulation <- var_out[[input$variable]]
  
  if (input$aggregation=="day" & input$flux_amount=="flux") simulation <- aggregate(simulation, as.Date(time(simulation)), mean, na.rm=T) 
  if (input$aggregation=="day" & input$flux_amount=="amount") simulation <- aggregate(simulation, as.Date(time(simulation)), sum, na.rm=F)
  if (input$aggregation=="month" & input$flux_amount=="flux") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), mean, na.rm=T)
    observation <- aggregate(observation, as.yearmon(time(observation)), mean, na.rm=T)
  } 
  if (input$aggregation=="month" & input$flux_amount=="amount") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), sum, na.rm=F)
    observation <- aggregate(observation, as.yearmon(time(observation)), sum, na.rm=F)
  } 
  
 # data <- merge(observation, simulation)
  
  if (input$cum == "cumulated over time")
  {
    if (input$variable=="evapotranspiration" | input$variable=="sensible_heat_flux_in_air" | input$variable=="latent_heat_flux_in_air") {
      data <- merge(observation, simulation)
      data <- window(x = data, start = as.Date("30-04-2011",format="%d-%m-%Y"), end = as.Date("17-04-2013", format="%d-%m-%Y"))
      data <- zoo(na.approx.default(data), time(data))
      data <- cumsum(data) 
    } else {
      data <- merge(observation, simulation)
      data <- data[!is.na(data$observation),]
      data <- cumsum(data)
    }

    
    dygraph(data, ylab=paste("[",units,"]",sep="")) %>%
      dyRangeSelector() %>%
      dyRoller()
  } else {
    data <- merge(observation, simulation)
    
    dygraph(data, ylab=paste("[",units,"]",sep="")) %>%
      dyRangeSelector() %>%
      dyRoller()
  }
 
})

```
  
***

####Summary Table on Goodness of Fit (GOF)

Measures for GOF are given for seasons and for the whole data series. Calculation were performed with the hydroGOF R-Package. Type ?gof in RStudio for information on specific GOFs.

```{r, echo=FALSE}

renderDataTable({
 if (input$aggregation=="hour" | input$aggregation=="day")
  {
    observation <- obs[[input$aggregation]][,input$variable]
  } else observation <- obs[["day"]][,input$variable]
  
  simulation <- var_out[[input$variable]]
  
 if (input$aggregation=="day" & input$flux_amount=="flux") simulation <- aggregate(simulation, as.Date(time(simulation)), mean, na.rm=T) 
  if (input$aggregation=="day" & input$flux_amount=="amount") simulation <- aggregate(simulation, as.Date(time(simulation)), sum, na.rm=F)
  if (input$aggregation=="month" & input$flux_amount=="flux") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), mean, na.rm=T)
    observation <- aggregate(observation, as.yearmon(time(observation)), mean, na.rm=T)
  } 
  if (input$aggregation=="month" & input$flux_amount=="amount") 
  {
    simulation <- aggregate(simulation, as.yearmon(time(simulation)), sum, na.rm=F)
    observation <- aggregate(observation, as.yearmon(time(observation)), sum, na.rm=F)
  } 
  
  data <- merge(observation, simulation)
  
  gofs <- gof(sim = data$simulation, obs=data$observation, na.rm = T)
  gofs <- as.data.frame(gofs)
  names(gofs) <- "YEAR"
  gofs$GOF <- dimnames(gofs)[[1]]
  
  mon <- as.numeric(format(time(data), "%m"))
  
  data_djf <-  data[mon==12 | mon==1 | mon==2,]
  gofs$DJF <-  c(gof(sim = data_djf$simulation, obs=data_djf$observation, na.rm = T))
  data_mam <-  data[mon==3 | mon==4 | mon==5,]
  gofs$MAM <-  c(gof(sim = data_mam$simulation, obs=data_mam$observation, na.rm = T))
  data_jja <-  data[mon==6 | mon==7 | mon==8,]
  gofs$JJA <-  c(gof(sim = data_jja$simulation, obs=data_jja$observation, na.rm = T))
  data_son <-  data[mon==9 | mon==10 | mon==11,]
  gofs$SON <-  c(gof(sim = data_son$simulation, obs=data_son$observation, na.rm = T))
  
  gofs <- gofs[,c(2,3,4,5,6,1)]

}, options = list(pageLength=5, lengthMenu=c(5, 10, 15, 20)))

```

***
